---
title: "CVM: Constrained variational optimization model with factorial designs"
author: "haiyan yu"
date: "7/16/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This document presents the stream of data processing, and the dignosis of the model. The four parts of diagnosis consist of discrepancy for blance check, trajectories of sampling, KLD for sampling compressiveness, parameter of the estimation (informativeness)  and the value of both the  compressiveness and  the informativeness. 
causal variational model
1,  dataxx[Treat.df == 1,"y"]):   total samples, not only the treatment group data, cwdf_ebal;
  
2,  cwdf_ebal[Treat.df == 1,"y"]):  only the treatment group data, cwdf_ebal;
    cwdf_ebalT <- cwdf_ebal[treatment == 1,]
    
3, weights for the control, not selected  
  
# Data preperation
```{r}
library("roxygen2")
library("readxl")
#library("CORopt")
library("cvmfd")
library(LaplacesDemon)
library(xtable)
#########
data <-
 suppressWarnings(data <-read_excel("~/Downloads/Rpkg/CORopt/data/USyu_AB_Med0UA1c_test.xlsx"))
#summary(data)#1: over 30; 0 :less 30
ls(data)
names(data)
head(data, 1)
nrow(data)
df.ctl<-data[data$metformin==0 &data$glyburide==0&data$`glyburide-metformin`==0,]
nrow(df.ctl)
#table(data$race,data$age)
table(data$age,data$readmitted)
#table(data$race,data$readmitted)
datax <- data[, c(6:21)]
df.sample<-head(data[, c(6:21)][, c(4,1:3,7,12,13:15)],8)
df.samplea3<-head(data[, c(6:21)][data$`glyburide-metformin`==2, c(4,1:3,7,12,13:15)],2)
df.samplea0<-head(data[, c(6:21)][data$`glyburide-metformin`==0&data$metformin==0&data$glyburide==0, c(4,1:3,7,12,13:15)],2)
xtable(df.sample)
xtable(df.samplea3)
xtable(df.samplea0)
names(datax) <-
  c(
    "x1",
    "x2",
    "x3",
    "x4",
    "x5",
    "x6",
    "x7",
    "x8",
    "x9",
    "x10",
    "x11",
    "x12",
    "a1",
    "a2",
    "a3",
    "y"
  )
head(datax)
##age =x4
table(datax$x4)
```

# Data Stream

Since there are missing and factor ('other') in the variables 'x2', those rows are removed by

```{r}
datax<-datax[datax$x2!='Other',]
datax<-datax[datax$x2!='?',]
#cwdf_ebal$x2<-as.numeric(cwdf_ebal$x2)
datax$x2<-as.numeric(datax$x2)
datax <- datax[complete.cases(datax), ]
```
# Data processing

```{r}
head(datax)
dataxx <- datax
dataxx[dataxx$a1 != 0, "a1"] <- 1
dataxx[dataxx$a2 != 0, "a2"] <- 1
dataxx[dataxx$a3 != 0, "a3"] <- 1
dataxx[, "A"] <- 0
dataxx[dataxx$a1 == 1, "A"] <- 1
dataxx[dataxx$a2 == 1, "A"] <- 2
dataxx[dataxx$a3 == 1, "A"] <- 3
#######
dataxx <- data.frame(dataxx)#summary(cweight) Inf
table(dataxx$A)
nrow(dataxx)
#######
```
## Cweight: call for caseweight

```{r}
cweight_df <- data.frame(dataxx)
for (i in seq(1:3)) {
  dataxy <- (dataxx[, c(1:12, 12 + i)])
  head(dataxy)
  names(dataxy) <-
    c("x1",
      "x2",
      "x3",
      "x4",
      "x5",
      "x6",
      "x7",
      "x8",
      "x9",
      "x10",
      "x11",
      "x12",
      "a")
  cor_temp <- caseweight(dataxy)
  #rename, denominator = in caseweight
  #dataxy$sw <- c.weight
  cweight_df <- cbind(cweight_df, cor_temp)
}
head(cweight_df)
names(cweight_df) <-
  c(
    "x1",
    "x2",
    "x3",
    "x4",
    "x5",
    "x6",
    "x7",
    "x8",
    "x9",
    "x10",
    "x11",
    "x12",
    "a1",
    "a2",
    "a3",
    "y",
       "A",
    "sw1",
    "sw2",
    "sw3" 
  )
head(cweight_df)
######
length(cweight_df$sw1)
```


#Discrepancy for blance check

```{r}

#############sw: weight for binary treatment with propensity score, not ebal
for (i in seq(1:3)) {
  dataxw <- cweight_df[, c(12 + i, 16 + i)]
  head(dataxw)
  wgtdensityplot(dataxw)
}

```


###Block

```{r}
head(cweight_df)
df.cbd<-cweight_df
table(df.cbd$x4)
df.cbd<-cweight_df
df.cbd[df.cbd$x4<=4,"block"]<-1
df.cbd[df.cbd$x4==5,"block"]<-2
df.cbd[df.cbd$x4==6,"block"]<-3
df.cbd[df.cbd$x4==7,"block"]<-4
df.cbd[df.cbd$x4==8 |df.cbd$x4==9,"block"]<-5
table(df.cbd$block)
table(df.cbd$block,df.cbd$x4)
table(df.cbd$block,df.cbd$A)
```

df.cbd[df.cbd$x4<=4,"block"]<-1
df.cbd[df.cbd$x4==5,"block"]<-2
df.cbd[df.cbd$x4==6,"block"]<-3
df.cbd[df.cbd$x4==7,"block"]<-4
df.cbd[df.cbd$x4==8 |df.cbd$x4==9,"block"]<-5
  

```{r}
library(reshape2)
  dfmean <- data.frame()
  dfvar <- data.frame()
  #ti<-4
  for (ti in seq(1:4)) {
    for (bi in seq(1:5)) {
      df.block <- df.cbd[df.cbd$block == bi, ]
      df.men <- df.block[df.block$A == (ti - 1), "y"]
      temp <- mean(df.men)
      dfmean <- rbind(dfmean, temp)
      tempvar <- var(df.men)
      dfvar <- rbind(dfvar, tempvar)
    }
  }

  names(dfmean) <- c("mean")
  names(dfvar) <- c("var")
  mat.mea <- round(dfmean$mean, 3)
  mat.var <- round(dfvar$var, 3)
  mat.mean <- matrix(mat.mea, nrow = 5, ncol = 4)
  mat.var <- matrix(mat.var, nrow = 5, ncol = 4)
  mat.mvar <- cbind(mat.mean, mat.var)
  print(mat.mvar)
  dat <- melt(t(as.matrix(mat.mean)))
  datvar <- melt(t(as.matrix(mat.var)))
  dat.mvar <- cbind(dat, datvar[, 3])
  print(dat.mvar)
  names(dat.mvar) <- c("Var1", "Var2", "mean", "Var")
  
    blockplot(dat)
    
   pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/blockplot.pdf", width = 5, height = 4.8)
  blockplot(dat)
   dev.off()
#mat.mean<-mat.mvar[,c(1:4)]

```

```{r}

{
p <- ggplot(dat.mvar, aes(x=Var2, y=mean, fill=as.factor(Var1))) + 
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-(Var/4), ymax=mean+(Var)/4), width=.2,
                 position=position_dodge(.9)) + scale_fill_brewer(palette="Paired") + theme_minimal()+
  ylim(0, 1.0)+
  xlab("Subclass")+ylab("Treatment response")+ labs(fill = "Treatment")
print(p)#;Stratum
 
#save(p) 
ggsave(filename="response.pdf", plot=p, width = 5, height = 4.8, 
 units = "in") # other options c("in", "cm", "mm"), 
}
print(dat.mvar)
```

```{r}
   print("###############LR with dual responses################")

  df.lr<-dat
  for (ind in seq(1:20)) {
    if(df.lr[ind,"Var1"]==1){
    df.lr[ind,"x1"]<--1
    df.lr[ind,"x2"]<--1
  }else if(df.lr[ind,"Var1"]==2){
    df.lr[ind,"x1"]<--1
    df.lr[ind,"x2"]<-1
  }else if(df.lr[ind,"Var1"]==3){
    df.lr[ind,"x1"]<-1
    df.lr[ind,"x2"]<--1
  }else{
    df.lr[ind,"x1"]<-1
    df.lr[ind,"x2"]<-1
  }
}
  ##LR
    lrq.mat<-lm(value~x1+x2+  I(x1^2)+I(x2^2)+x1*x2, data = df.lr)
  print(summary(lrq.mat))
  #xtable(aov(lrq.mat))
  res.aov <- aov(value~x1+x2+x1*x2, data = df.lr)
   print(summary(res.aov))
print( xtable(aov(res.aov),digits = 4))
       print("################above: x1+x2+x1*x2################")
   lrq.mat<-lm(value~x1+x2+  I(x1^2)+I(x2^2)+x1*x2+Var2+x1*Var2+x2*Var2, data = df.lr)
  print(summary(lrq.mat)) 
   res.aov <- aov(value~x1+x2+x1*x2+x1*Var2+x2*Var2, data = df.lr)
   print(summary(res.aov))
print( xtable(aov(res.aov),digits = 4))

```
```{r}

#####
#names(ggplot.df)<-c("group","rep1","rep2","rep1se","rep2se")
 # line.df<-ggplot.df[,1:3]
#  line.dfrep<-ggplot.df[,2]-ggplot.df[,3]
   print(pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/str.pdf", width = 5, height = 4.8))
# respsurfaceplot5s(mat.mean) 
  # xlab = c("Subclass") # Stratum xlab = c("Blocks")#, ylab = expression(V(A))
   #        ylab=c("Objective V(A,Y)")
# pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/str.pdf", width = 5, height = 4.8)
# dev.off()
  respsurfaceplot5s(mat.mean) 
```
  

  
```{r}
head(dat.mvar)
dat.mvar$Cell<-dat.mvar$Var1+(dat.mvar$Var2-1)*4

    resp.df<-dat.mvar[,c(5,3,4)]
    
```

## Solution for each blocks

```{r}
head(dat.mvar)
#opt.bmse<-optcretria(dat.mvar,"min")
opt.bmse<-optcretria5s(dat.mvar,"max")
head(opt.bmse)
xtable(opt.bmse)
```
##
ebalnce use low corratina variables
```{r}
head(df.cbd)
 cor(df.cbd[, c(1:12)])
  cor(df.cbd[, c(1:3,7,12)])
```

```{r,warning=FALSE,echo=FALSE,include=FALSE,comment=NA}
library(LaplacesDemon)
table(df.cbd$block,df.cbd$A)
df.cbd$Cell<-(df.cbd$A+1)+(df.cbd$block-1)*4
head(df.cbd,1)
table(df.cbd$Cell)
df.mean<-data.frame()
dist.out<-data.frame()
    kldconv.df<-data.frame()
    kldconv.dfc<-data.frame()
    
for (bi in seq(1:5)) {
  eb.dfb<-df.cbd[df.cbd$block==bi,]
  for (ti in seq(1:3)) {
    table(eb.dfb$A)
      eb.dfbt<-eb.dfb[eb.dfb$A==(ti-1)|eb.dfb$A==3,]
      eb.dfbt$A<-eb.dfbt$A+1
      eb.dfbt[eb.dfbt$A!=4,"T"]<-0
      eb.dfbt[eb.dfbt$A==4,"T"]<-1
head(eb.dfbt)
table(eb.dfbt$Cell)
table(eb.dfbt$T)
## Weighting for two groups
#############a1, control weight##################################
library("ebal")
cwdf_ebal<-eb.dfbt

head(cwdf_ebal)
####
cwdf_ebal<-data.frame(cwdf_ebal)
cwdfmis<-complete.cases(cwdf_ebal)
cmisdf<-cwdf_ebal[!cwdfmis,]
head(cmisdf)
cwdf_ebal<-na.omit(cwdf_ebal)
#head(cwdf_ebal)
cwdf_ebalraw<-cwdf_ebal
#cwdf_ebal<-cwdf_ebal[is.na(cwdf_ebal$x2),]
treatment   <- cwdf_ebal[, "T"]
 table(treatment)
 #####16:y
 X           <- cwdf_ebal[, c(1:12,23,16)]
  treatment <- data.matrix(treatment)
  X<-preprocess(X)
#eb.out <- ebalance(X[,13],#Treatment =
#                    X[, c(1:2)])#X =
#KLD for sampling compressiveness
########Iterations
max.iterations=20#1000
nq<-nrow(X[,])
temp<-data.frame(rep(1/nq, nq))
q<-(temp[1,])
ntrt<-nrow(eb.dfbt)-sum(eb.dfbt$T)
kldconv<-kldc(X,ntrt,max.iterations) 

#Parameter of the estimation (informativeness)
#mu0 for the estimation (informativeness), 
#```{r,warning=false}
ymu0<-data.frame(q)*(X[,14])
ymu0mean<-sum(ymu0)/sum(q)
ymu0mean
df.mean<-meanfun(X,max.iterations)
dist.out<-distcovariate(X)
########
df.mean
#plot(tempmu$mu0)
  head(kldconv)
kldconv.df<-rbind(kldconv.df,round(kldconv[max.iterations,],3))
kldconv.dfc<-rbind(kldconv.dfc,c(bi,ti,round(kldconv[max.iterations,],3)))
names(kldconv.dfc)<-c("bi","ti","kld")
  }
  }
names(kldconv.df)<-c("kld")
kldconv.df
kldconv.dfc
dist.out
```

```{r}
dist.out<-data.frame(dist.out)
names(dist.out)<-c("block","treatment","dist")
#temp<-dat.mvar[c(13:17),c(1:3)]
temp<-dat.mvar[c(4,8,12,16,20),c(1:3)]
names(temp)<-c("treatment","block","dist")
temp$dist<-0
temp<-temp[,c(2,1,3)]
dist.outdf<-rbind(dist.out,temp)
dist.outdf$Cell<-(dist.outdf$block-1)*4+dist.outdf$treatment
dist.outdf<-dist.outdf[order(dist.outdf$Cell),]
dist.outdf
```
```{r}
kld.neg<-data.frame()
kld.neg<-cbind(kldconv.dfc$bi,kldconv.dfc$ti,-(kldconv.dfc$kld))
kld.neg<-data.frame(kld.neg)
names(kld.neg)<-c("block","treatment","negkld")
#temp<-dat.mvar[c(13:16),c(1:3)]
#names(temp)<-c("block","treatment","negkld")
temp<-dat.mvar[c(4,8,12,16,20),c(1:3)]
names(temp)<-c("treatment","block","negkld")
temp$dist<-0
temp<-temp[,c(2,1,3)]
temp$negkld<-0
kld.neg<-rbind(kld.neg,temp)
kld.neg$Cell<-(kld.neg$block-1)*4+kld.neg$treatment
kld.neg<-kld.neg[order(kld.neg$Cell),]
kld.neg
```
```{r}
resp.df
#0:2, vs. 3
df.mean
df.wgt<-rbind(df.mean,resp.df[c(4,8,12,16,20),])

df.wgt<-round(df.wgt,3)
df.wgt<-df.wgt[order(df.wgt$Cell),]
df.wgt
```

```{r}
dat.mvar<-df.wgt
#Va1:Treat; Var2: Blcok
head(dat.mvar)
dat.mvar2<-dat.mvar
dat.mvar2$Var1<-rep(1:4,5)
dat.mvar2$Var2<-rep(1:5,each=4)
#opt.bmse<-optcretria(dat.mvar,"min")
#opt.bmse<-optcretria(dat.mvar,"max")
#head(opt.bmse)
#xtable(opt.bmse)
#opt.cmr<-mean(opt.bmse$mean)
#opt.cmr
{
p <- ggplot(dat.mvar2, aes(x=Var2, y=mean, fill=as.factor(Var1))) + 
   geom_bar(stat="identity", position=position_dodge()) +
  geom_errorbar(aes(ymin=mean-(Var)/4, ymax=mean+(Var)/4), width=.2,
                 position=position_dodge(.9)) + scale_fill_brewer(palette="Paired") + theme_minimal()+
  xlab("Subclass")+ylab("Treatment response")+ labs(fill = "Treatment")
print(p)#;Stratum
 
#save(p) 
ggsave(filename="responsewt.pdf", plot=p, width = 5, height = 4.8, 
 units = "in") # other options c("in", "cm", "mm"), 
}
 print(dat.mvar2)
 
   mat.meanwt <- matrix(dat.mvar2$mean, nrow = 4, ncol = 5)
 datwt <- melt((as.matrix(mat.meanwt)))
#  datvar <- melt(t(as.matrix(mat.var)))
#  dat.mvar <- cbind(dat, datvar[, 3])
 # print(dat.mvar)
 # names(dat.mvar) <- c("Var1", "Var2", "mean", "Var")
 
    blockplot(datwt)
    
    {
   pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/blockplotwt.pdf", width = 5, height = 4.8)
  blockplot(datwt)
   dev.off()  
}
   
```

```{r}
mat.assign<-matrixassign5s(mat.mean)
opt.bmse<-matrixassign5s(mat.mean)
```

```{r}
#df.sol
paretoplotpositive5s(resp.df,opt.bmse)
opt.bmse[,c(2:3)]
#####
mat.mean<-matrix(df.wgt$mean,nrow = 5, ncol = 4)
mat.assign<-matrixassign5s((mat.mean))
df.sol<-mat.assign
#paretoplot(df.wgt,df.sol)
df.wgt<-data.frame(df.wgt)
#opt.bmse2<-df.wgt[df.wgt$Cell==df.sol$Cell,]
opt.bmse2<-df.wgt[c(1,7,11,14,20),]
paretoplotpositive5s(df.wgt,(opt.bmse2))
df.out<-df.sol[,c(2,4,4,3,1)]
library(xtable)
xtable(df.out)

```

###KLD as secondary responses
```{r}
head(kld.neg)
reps.kld<-cbind(resp.df,kld.neg$negkld)
paretodf<-reps.kld[,c(1,2,4)]
head(paretodf)
#names(paretodf)
#kldopt.bmse<-
  #matrixassign(kld.mat)[c(1:4),]
pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/paretowt.pdf", width = 5, height = 4.8)
paretoplot(paretodf,opt.bmse)
  dev.off()
kld.mat<-matrix( paretodf[,3],nrow = 4)


df.wgt
names(paretodf)<-c("Cell","mean","negkld")

paretodf$objv<-round(paretodf$mean+0.001*paretodf[,3],2)
paretodf

```
```{r}
df.vmax<-data.frame()
mat.mean<-matrix(df.wgt$mean,nrow = 5, ncol = 4)
for(bi in seq(1:4)){
  ggplot.df<-data.frame(mat.mean[bi,])
  names(ggplot.df)<-c("mean")
opt.vmax<-ggplot.df[ggplot.df$mean==max(ggplot.df$mean),]
opt.vmax$cretria<-"max"
opt.vmax$optv<-max(ggplot.df$mean)
df.vmax<-rbind(df.vmax,opt.vmax$optv)
}
df.vmax

```

```{r}
head(mat.mean)
# dev.off()
# respsurfaceplot5s(mat.mean)
mat.mean.wt<-matrix(df.wgt$mean,nrow=4)
mat.mean.w<-t(mat.mean.wt)
#respsurfaceplot5s(mat.mean.w)
print(pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/strwt.pdf", width = 5, height = 4.8))
#pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/strwt.pdf", width = 5, height = 4.8)
 #dev.off()
 respsurfaceplot5s(mat.mean.w)
```




```{r}
#df.wgt
datvar<-melt(t(as.matrix(mat.mean.w)))
dat<-datvar
  df.lr<-dat
  for (ind in seq(1:20)) {
    if(df.lr[ind,"Var1"]==1){
    df.lr[ind,"x1"]<--1
    df.lr[ind,"x2"]<--1
  }else if(df.lr[ind,"Var1"]==2){
    df.lr[ind,"x1"]<--1
    df.lr[ind,"x2"]<-1
  }else if(df.lr[ind,"Var1"]==3){
    df.lr[ind,"x1"]<-1
    df.lr[ind,"x2"]<--1
  }else{
    df.lr[ind,"x1"]<-1
    df.lr[ind,"x2"]<-1
  }
}
  ##LR
    lrq.mat<-lm(value~x1+x2+  I(x1^2)+I(x2^2)+x1*x2, data = df.lr)
  print(summary(lrq.mat))
       print("################above: x1+x2+x1*x2################")
   lrq.mat<-lm(value~x1+x2+  I(x1^2)+I(x2^2)+x1*x2+Var2, data = df.lr)
  print(summary(lrq.mat))
  print( xtable(aov(lrq.mat),digits = 4))
   lrq.mat<-lm(value~x1+x2+  I(x1^2)+I(x2^2)+x1*x2+Var2+Var2*x1+Var2*x2, data = df.lr)
  print(summary(lrq.mat))
   print( xtable(aov(lrq.mat),digits = 4))

```

```{r}
kldconv.df
head(X)
head(X[, c(1:3,7,12)],1)
```
##Variance
  The weighted variance is the $\Sigma (A_j, B_l)$ is the individial responses of 
    each cells. That is      estimated variance  
    $${\hat \Sigma _i}({\hat V_l}) =\sum\nolimits_{i = 1}^{{N_{il}}} {\left( {\phi _i^2{{\hat \Sigma }_{il}}} \right)}.$$ 
    For $ Avg(\hat \Sigma({{\hat V_l}}))$, it  is the variance of the model.  In the model, all of them assumed to be homoscedasticity.  
    $$
    \hat V=\bar V+ \epsilon= \mu_0+ \beta_l+\tau_j+\epsilon, \epsilon \sim (0, \Sigma({{\hat V_l}}))
    $$
    The bias is the confounding error, $e_l= \hat V_l-\bar V$, 
    And the squared  bias is   
    $${\mathop{ \Sigma}} ({{\hat V_l(A, \phi)}}) = \frac{1}{{b-1}} \sum\limits_{i= 1}^b {  {\left( {{{\hat V_l(A, \phi)}}     - {{\hat V(A, \phi) }}} \right)^2} }.$$ 
  MSE: $$\Sigma =Avg(\hat \Sigma({{\hat V_l}})) 
        + \left( {\frac{1}{{b }}} + 1\right) 
        {\mathop{ \Sigma}} ({{\hat V_l}}),
     $$
```{r}
# estimated variance  of ecah cell

```


##Negative lines

```{r}
resp.negdf<-resp.df
resp.negdf$Var<-(-resp.negdf$Var)
opt.bmseneg<-opt.bmse
paretoplot5s(resp.negdf,opt.bmse)
opt.bmse[,c(2:3)]
   pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/pareto.pdf", width = 5, height = 4.8)
paretoplot5s(resp.negdf,opt.bmse)
 dev.off()
#####
mat.mean<-matrix(df.wgt$mean,nrow = 5, ncol = 4)
#mat.assign<-matrixassign(t(mat.mean))
mat.assign<-matrixassign5s((mat.mean))
df.sol<-mat.assign
#paretoplot(df.wgt,df.sol)
df.wgt<-data.frame(df.wgt)
#opt.bmse2<-df.wgt[df.wgt$Cell==df.sol$Cell,]
#opt.bmse<-df.wgt[c(1,7,10,16),]
opt.bmse<-df.wgt[c(3,6,10,15, 20),]
df.wgtneg<-df.wgt
df.wgtneg$Var<- (-df.wgtneg$Var)
opt.bmse2<-opt.bmse
opt.bmse2$Var<-(-opt.bmse2$Var)
paretoplot5s(df.wgtneg,opt.bmse2)
   pdf(file ="~/Downloads/Rpkg/cvmfd/man_ffd/paretowt.pdf", width = 5, height = 4.8)
paretoplot5s(df.wgtneg,opt.bmse2)
 dev.off()
#paretoplotpositive5s(df.wgtneg,opt.bmse2)
df.out<-df.sol[,c(2,4,1,3)]
library(xtable)
xtable(df.out)
```


```{r}
ggplot(data=dat.mvar, aes(x=seq(1:20), y=Var))  +
    geom_line()
# Most basic error bar
ggplot(dat.mvar) +
    geom_bar( aes(x=seq(1:20), y=mean), stat="identity", fill="skyblue", alpha=0.7) +
    geom_errorbar( aes(x=seq(1:20), ymin=mean-sqrt(Var), ymax=mean+sqrt(Var)), width=0.4, colour="orange", alpha=0.9, size=1.3)

ggplot(dat.mvar) +
    geom_line( aes(x=seq(1:20), y=mean))  +
    annotate(geom="text", x=4, y=0.65, label="mean",
              color="red")+
    geom_line( aes(x=seq(1:20), y=Var))  +
    annotate(geom="text", x=4, y=0.17, label="Variance",
              color="red")+
  xlab("cell") + ylab("value")+ labs(fill = "Response")+
  theme(legend.position="topright",legend.title = element_text(color = "blue", size = 10),
          legend.text = element_text(color = "red"))+
   geom_hline(yintercept = 0.25,  colour = c(2),lty=c(2))+
  geom_hline(yintercept = 0.11,  colour = c(2),lty=c(2))+
  geom_hline(yintercept = 0.7,  colour = c(3),lty=c(2))+
  theme_bw()

```
